### 2021-08-31 paper.Rmd
done with NN example

\begin{figure*}
  \centering
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-orange.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-green.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-purple.png}
  \caption{A grand tour run on the prediction boundaries of a radial support vector machine. (Left) The prediction region for points classified as orange produces a slice of a cube. (Middle) The prediction region for points classified as green produces another slice of the cube. (Right) The complete prediction region shows the points classified as purple are embedded within the green slice. Adapted from \cite{Wickham2015-do}, Figure 6.}
  \label{fig:svm-tour}
\end{figure*}

@Wickham2015-do espouses the tour as a key component of their approach for visualizing models in data space. They propose using the tour to explore the high dimensional surfaces produced by model fits instead of simple summary statistics.  In Figure \ref{fig:svm-tour} samples have been taken along the prediction region (i.e. the value the model predicts over a grid of observations) of a 3-$d$ support vector machine used to classify three different classes (green, orange purple), by touring over the prediction region we can see how the classifier splits the decision boundaries.

@@

The grand tour along with direct interaction techniques has been proposed as a technique for understanding the training of deep neural network models [@Li2020-kg]. They proposed a novel method for aligning the output of different layers by interpolating the output of different layers of a deep neural network via the the grand tour. They also apply the grand tour to explore the changes in single layers of the network for each training epoch. For example, by the running tour over the softmax layer outputs of a classification model, an analyst may understand where in the training confusion between classes occur and gain a view of model performance (Figure \ref{fig:tour-nn}). Similarly, the difference between training and test sets can be assessed through side-by-side linked tours of layer outputs. @li_toward_2020 extends this idea by first reducing the dimensionality of output layers with UMAP [@mcinnes2020umap] and then using the grand tour with manual controls over 15 dimensional embeddings to understand layer topology.

>>>>

\begin{figure*}
  \centering
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-orange.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-green.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-purple.png}
  \caption{A grand tour using GGobi software to explore the prediction boundaries of a radial support vector machine. The prediction region for points classified as orange produces a slice of a cube (left). The prediction region for points classified as green produces another slice of the cube (middle). The complete prediction region shows the points classified as purple are embedded within the green slice (right). Adapted from \cite{Wickham2015-do}, Figure 6.}
  \label{fig:svm-tour}
\end{figure*}

@Wickham2015-do espouses the tour as a key component of their approach for visualizing models in data space. They propose using the tour to explore the high dimensional surfaces produced by model fits instead of simple summary statistics.  In Figure \ref{fig:svm-tour} samples have been taken along the prediction region (i.e. the value the model predicts over a grid of observations) of a 3D support vector machine used to classify three different classes (green, orange purple). By touring over the prediction region, we can see how the classifier splits the decision boundaries.

@@

The grand tour along with direct interaction techniques has been proposed as a technique for understanding the training of deep neural network models [@Li2020-kg]. They propose a novel method for aligning the output of different layers by interpolating the output of different layers of a deep neural network via the the grand tour. They also apply the grand tour to explore the changes in single layers of the network for each training epoch. For example, by running the tour over the softmax layer outputs of a classification model, an analyst may understand where in the training confusion between classes occur and gain a view of the model performance (Figure \ref{fig:tour-nn}). Similarly, the difference between training and test sets can be assessed through side-by-side linked tours of layer outputs. @li_toward_2020 extends this idea by first reducing the dimensionality of output layers with UMAP [@mcinnes2020umap] and then using the grand tour with manual controls over 15 dimensional embeddings to understand layer topology.
